Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-23 main.tex
Addressing comments about generator level cuts for signal and bg

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{align}
M_R &= \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
M_T^R &= \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
\end{align}
 for $E_{Z,h}$ and $\vec{p}_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$, respectively.
      Representative kinematic
  distributions of these variables for signal events of $\mu=1$ TeV Higgsinos
  NLSP and a $M_1=25$ GeV Bino LSP, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
  $\slashed{E}_{T}$,  and  $m_{\ell^+\ell^-}$cuts.   
  \Shufang{BG generator level mll and MET cut (MET bigger tan 100 GeV), or cut
    level mll and MET cut (MET bigger than 400 GEV)? Both signal and
  backgrounds?} The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which is consistent with what we would expect as
  it corresponds to the mass difference between the NLSP and LSP.  The $tt$
  background peaks around 500 GeV, while the distribution of $tbW$ background
  almost overlaps with that of the signal process.  Similar behaviour also
  appears for $M_T^R$ distributions.  
  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

@@

For each signal mass combination and each background process, we preselected
events that passed the lepton trigger, contained two SFOS leptons and two
$b$-tagged jets, and calculated a number of kinematic variables for each event.
  \Shufang{So singal event does not have mll and MET parton level cuts while BG events have those two cuts. right?}   We then
placed these kinematic variables in an array, with each row corresponding to an
event, and the columns corresponding to the kinematic variables. A mixture of
low-level and high level kinematic variables was shown to have the greatest
effectiveness. The kinematic variables chosen were $m_{\ell\ell}$, $m_{bb}$,
$M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic transverse energy $H_T$,
and transverse momenta of individual final state leptons and $b$-quarks:
$p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We then divided
the generated events into training and test sets, with the training set
comprising 75\% of signal events and 30\% of background events.  We used the
\texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
A boosted decision tree classifier was trained with 1000 weak learners and a
learning rate of 0.025.

@@

\begin{figure}[h]
\centering
%\includegraphics[width=0.6\textwidth]{images/combined.pdf}
\includegraphics[width=0.6\textwidth]{images/dm_100_TeV_contours.png}

\caption{ Discovery (red) and exclusion (blue) contours for the traditional
  cut-and-count analysis (solid) and boosted decision tree analysis (dashed),
  for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
\Adarsh{  I could change the xlabel
to $\mu$ instead of $|\mu|$, but isn't $|\mu|$ more accurate, since $\mu$ can
be positive or negative?} \Shufang{Yes, change to $\mu$.  Sign of mu has a small effect.  Since we use positive mu, let's label it this way.}
}

>>>>

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{align}
M_R &= \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
M_T^R &= \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
\end{align}
 for $E_{Z,h}$ and $\vec{p}_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$, respectively.
      Representative kinematic
  distributions of these variables for signal events of $\mu=1$ TeV Higgsinos
  NLSP and a $M_1=25$ GeV Bino LSP, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
  $\slashed{E}_{T}$,  and  $m_{\ell^+\ell^-}$cuts.   
  \Shufang{BG generator level mll and MET cut (MET bigger tan 100 GeV), or cut
    level mll and MET cut (MET bigger than 400 GEV)? Both signal and
  backgrounds?} \Adarsh{The plots in figure 2 show distributions at the reconstructed level,
  so they have the generator level cuts and the reconstructed level cuts. 
  For the signal, no generator-level cuts are applied.
  For the background, the $80 < m_{ll} < 100 $ GeV and  $\met > 100$ GeV
  generator level cuts are applied.}
  The distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which is consistent with what we would expect as
  it corresponds to the mass difference between the NLSP and LSP.  The $tt$
  background peaks around 500 GeV, while the distribution of $tbW$ background
  almost overlaps with that of the signal process.  Similar behaviour also
  appears for $M_T^R$ distributions.  
  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

@@

For each signal mass combination and each background process, we preselected
events that passed the lepton trigger, contained two SFOS leptons and two
$b$-tagged jets, and calculated a number of kinematic variables for each event.
  \Shufang{So singal event does not have mll and MET parton level cuts 
  while BG events have those two cuts. right?} \Adarsh{Right.}   We then
placed these kinematic variables in an array, with each row corresponding to an
event, and the columns corresponding to the kinematic variables. A mixture of
low-level and high level kinematic variables was shown to have the greatest
effectiveness. The kinematic variables chosen were $m_{\ell\ell}$, $m_{bb}$,
$M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic transverse energy $H_T$,
and transverse momenta of individual final state leptons and $b$-quarks:
$p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We then divided
the generated events into training and test sets, with the training set
comprising 75\% of signal events and 30\% of background events.  We used the
\texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
A boosted decision tree classifier was trained with 1000 weak learners and a
learning rate of 0.025.

@@

\begin{figure}[h]
\centering
%\includegraphics[width=0.6\textwidth]{images/dm_100_TeV_contours.png}
\input{images/dm_100_TeV_contours.pgf}

\caption{ Discovery (red) and exclusion (blue) contours for the traditional
  cut-and-count analysis (solid) and boosted decision tree analysis (dashed),
  for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
}
